### 2018-05-28 Paper/intro.tex
..

\paragraph{Our approach}
We present a strategy for identifying and screening uncertain model parameters
that are significantly less important that the rest, thereby reducing the
dimensionality of the problem and enabling the construction of a reduced-order
surrogate (ROS).  Our approach combines DGSMs and surrogate modeling in an
iterative manner.  To make maximum use of computational resources, batches of
model evaluations are performed iteratively, and convergence of our DGSM based
screening metric is tested successively. Moreover, the validation steps built
in our method enable monitoring the accuracy of the parameter-screening and the
constructed surrogate model.  Our approach is agnostic to the choice of
methodology for constructing the surrogate. However, in the present work, we
rely on sparse PCEs to demonstrate the suitability of the proposed strategy.

>>>>

\paragraph{Our approach}
We present a strategy for identifying and screening uncertain model parameters
that are significantly less important than the rest, thereby reducing the
dimensionality of the problem and enabling the construction of a reduced-order
surrogate (ROS).  Our approach combines DGSMs and surrogate modeling in an
iterative manner.  To make maximum use of computational resources, batches of
model evaluations are performed iteratively, and convergence of our DGSM based
screening metric is tested successively. Moreover, the validation steps built
in our method enable monitoring the accuracy of the parameter-screening and the
constructed surrogate model.  Our approach is agnostic to the choice of
methodology for constructing the surrogate. However, in the present work, we
rely on sparse PCEs to demonstrate the suitability of the proposed strategy.
